\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-22 4-5-interactive.Rmd
appendix

When dealing with spatio-temporal data, users may wish to make plots to learn the spatial distribution of a variable or to find patterns, such as trend or seasonality, in the time series. Combining these two types of plots with interactivity lets users link between points on the map and the corresponding time series to explore the spatial and temporal dimensions of the data simultaneously. Below is an example that describes the process of building an interactive graphic with \pkg{cubble} and \pkg{crosstalk}. This example explores the variation of monthly temperature range within the \code{climate_full} data.

@@

This plot can also be made using \pkg{cubble} and \pkg{leaflet}, in which case the temperature range is displayed as a small subplot upon clicking on the map. This procedure involves first creating the popup plots from the long form cubble as a vector and then adding these plots to a leaflet map created from the nested cubble, with \code{leafpop::addPopupGraphs()}:

# use the long form to create subplots for each station
df_id <- unique(clean$id)
p <- map(1:length(df_id), function(i){
  dt <- clean %>% filter(id == df_id[i])
  ggplot(dt) %>% ...
})

# create nested form leaflet map with temperature band as subplots
nested <- face_spatial(clean)
leaflet(nested) |>
  addTiles() |>
  addCircleMarkers(group = "a", ...) |>
  leafpop::addPopupGraphs(graph = p, ...)

Figure \ref{fig:interactive-popup} shows the same information as Figure \ref{fig:interactive-linking} but using leaflet and popups [@leafpop].

```{r interactive-popup, fig.align='center', echo = FALSE, out.width="45%", out.height="25%", fig.retina = 2, dpi = 300, fig.cap = "Same as Figure 11 except the temperature variation is now shown as a popup in the leaflet map.", fig.show='hold'}
knitr::include_graphics(here::here("figures/popup-mid.png"))
```

>>>>

Interactive graphics can be useful to make it possible to look at the data in a multiple of ways. This is especially important for spatiotemporal data, where we would like to interactively connect spatial and temporal displays. This example describes the process of building an interactive display with \pkg{cubble} and \pkg{crosstalk}. It explores the variation of monthly temperature range within the \code{climate_full} data.

<!--When dealing with spatio-temporal data, users may wish to make plots to learn the spatial distribution of a variable or to find patterns, such as trend or seasonality, in the time series. Combining these two types of plots with interactivity lets users link between points on the map and the corresponding time series to explore the spatial and temporal dimensions of the data simultaneously.-->

@@

### 2022-06-22 jss/appendix.Rmd
appendix

---
title: "Appendix to 'cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data'"
author: "Sherry Zhang, Dianne Cook, Ursula Laa, Nicolas Langrené, Patricia Menéndez"
date: '2022-06-14'
output:
  bookdown::pdf_document2:
    toc: false
    number_section: true

---

@@

>>>>

---
title: "Appendix to 'cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data'"
author: "Sherry Zhang, Dianne Cook, Ursula Laa, Nicolas Langrené, Patricia Menéndez"
date: '2022-06-14'
output:
  bookdown::pdf_document2:
    toc: false
    number_section: true
---

@@

# Extension to section 5.5: Interactive graphics

Figure XXX in this section can also be made using \pkg{cubble} and \pkg{leaflet}, in which case the temperature range is displayed as a small subplot upon clicking on the map. This procedure involves first creating the popup plots from the long form cubble as a vector and then adding these plots to a leaflet map created from the nested cubble, with \code{leafpop::addPopupGraphs()}:

``` r
# data pre-processing
clean <- climate_full %>% ...

# use the long form to create subplots for each station
df_id <- unique(clean$id)
p <- map(1:length(df_id), function(i){
  dt <- clean %>% filter(id == df_id[i])
  ggplot(dt) %>% ...
})

# create nested form leaflet map with temperature band as subplots
nested <- face_spatial(clean)
leaflet(nested) |>
  addTiles() |>
  addCircleMarkers(group = "a", ...) |>
  leafpop::addPopupGraphs(graph = p, ...)

```

Figure \ref{fig:interactive-popup} shows the same information as Figure XXX but using leaflet and popups [@leafpop].

```{r interactive-popup, fig.align='center', echo = FALSE, out.width="45%", out.height="25%", fig.retina = 2, dpi = 300, fig.cap = "Same as Figure 11 except the temperature variation is now shown as a popup in the leaflet map.", fig.show='hold'}
knitr::include_graphics(here::here("figures/popup-mid.png"))
```

### 2022-06-22 jss/cubble-jss.tex
appendix

When dealing with spatio-temporal data, users may wish to make plots to learn the spatial distribution of a variable or to find patterns, such as trend or seasonality, in the time series. Combining these two types of plots with interactivity lets users link between points on the map and the corresponding time series to explore the spatial and temporal dimensions of the data simultaneously. Below is an example that describes the process of building an interactive graphic with \pkg{cubble} and \pkg{crosstalk}. This example explores the variation of monthly temperature range within the \code{climate_full} data.

>>>>

Interactive graphics can be useful to make it possible to look at the data in a multiple of ways. This is especially important for spatiotemporal data, where we would like to interactively connect spatial and temporal displays. This example describes the process of building an interactive display with \pkg{cubble} and \pkg{crosstalk}. It explores the variation of monthly temperature range within the \code{climate_full} data.
